School accessibility  in Sao Paulo

### 2015-09-22 paper.Rmd
Add abstract!

---
title: "School accessibility in Sao Paulo"
author: "Ana Moreno and Robin Lovelace"
date: "Monday, September 21, 2015"
output: pdf_document
---

>>>>

---
title: "School accessibility  in Sao Paulo"
title: "School accessibility: a new index with a case study of enrollment and academic performance in Sao Paulo"
author: "Ana Moreno and Robin Lovelace"
date: "Monday, September 21, 2015"
output: pdf_document
---

# Abstract

Travel to school is an everyday reality for millions of young people around the world.
The mode, duration, levels

Access to high quality quality schools is highly variable across geographical
space so travel options are vital for ensuring a more equitable supply of
educational opportunity to diverse groups. Conversely, poor accessibility
to deprived area can reinforce social inequalities, with long-term implications.

Based on these emerging findings, this paper sets out a school accessibility index.
This index is based on current travel patterns, local travel infrastructure serving the school
catchment and the provision of travel services such as public transport links.
Using data from the Household Travel Survey (2007 and 2012), the School Census
and electronic card data, we apply this metric to schools in Sao Paulo.

Its impact on the social background of school attendees.
A wider aim of this paper is to explore the potential links between accessibility
and academic acheivement and opportunities.
